### 2024-06-19 out/01._Introduction/02._Moving_hallway_problem.tex
Fix errata

To observe (1) that \(S \subseteq L_t\) for every angle \(t \in [0, \omega]\), note that the sofa \(S\) is rotated initially by a clockwise angle of \(0\) and finally by \(\omega\) during its movement. By the intermediate value theorem, there is a moment where a copy of \(S\) is rotated clockwise by \(t\) inside \(L\). Push the rotated copy of \(S\) in \(L\) towards the positive \(x\) and \(y\) directions, until it makes contact with the outer walls \(x=1\) and \(y=1\) of \(L\). See this configuration in the perspective of \(S\) to conclude \(S \subseteq L_t\). To observe (2) and (3), note that the sofa \(S\) is initialy in \(L_H\) and finally in \(L_H\) rotated clockwise by \(\omega\); see the configurations in perspective of \(S\) ot conclude that \(S\) is in \(H\) and a translation of \(V_\omega\).

@@

Without loss of generality, we can translate the moving sofa \(S\) horizontally and assume that \(S\) is contained in \(V_\omega\), not its arbitrary translation.\footnote{Translating the moving sofa \(S\) may invalidate the initial condition \(S \subseteq L_H\). To resolve this, we relax the \Cref{def:sofa} of a moving sofa \(S\) in so that only some translation of \(S\) is required to be movable from \(L_H\) to \(L_V\) inside \(L\).} Then from (1), (2) and (3) above, we can always assume that \(S\) is contained in the intersection
\begin{equation}
\label{eqn:monotone}
\mathcal{M}(S) := H \cap V_\omega \cap \bigcap_{0 \leq t \leq \omega} L_t
\end{equation}
that we will define as the \emph{monotonization} of a moving sofa \(S\). The set \(\mathcal{M}(S)\) is also movable inside \(L\); observe that \(\mathcal{M}(S)\) is in each rotating hallway \(L_t\) of angle \(t \in [0, \omega]\), and see this in the perspective of the fixed hallway \(L\) instead of the moving hallway \(L_t\) and vary \(t\) from \(0\) to \(\omega\). So the monotonization \(\mathcal{M}(S)\) is a moving sofa containing \(S\) (\Cref{thm:monotonization-is-sofa})\footnote{This uses an implicit assumption that the intersection \(\mathcal{M}(S)\) should be connected. Indeed, \autocite{gerverMovingSofaCorner1992} assumes the connectedness of \(\mathcal{M}(S)\) in its proof of Theorem 1 of \autocite{gerverMovingSofaCorner1992} without further justification. We prove this assumption rigorously in \Cref{thm:monotonization-is-connected}.}, and we call such a sofa \(\mathcal{M}(S)\) from monotonization a \emph{monotone sofa} (\Cref{def:monotone-sofa}). Since any moving sofa \(S\) is contained in a larger monotone sofa \(\mathcal{M}(S)\), we only need to consider monotone sofas for the moving sofa problem.

>>>>

To observe (1) that \(S \subseteq L_t\) for every angle \(t \in [0, \omega]\), note that the sofa \(S\) is rotated initially by a clockwise angle of \(0\) and finally by \(\omega\) during its movement. By the intermediate value theorem, there is a moment where a copy of \(S\) is rotated clockwise by \(t\) inside \(L\). Push the rotated copy of \(S\) in \(L\) towards the positive \(x\) and \(y\) directions, until it makes contact with the outer walls \(x=1\) and \(y=1\) of \(L\). See this configuration in the perspective of \(S\) to conclude \(S \subseteq L_t\). To observe (2) and (3), note that the sofa \(S\) is initialy in \(L_H\) and finally in \(V_H\) rotated clockwise by \(\omega\); see the configurations in perspective of \(S\) to conclude that \(S\) is in \(H\) and a translation of \(V_\omega\).

@@

Without loss of generality, we can translate the moving sofa \(S\) horizontally and assume that \(S\) is contained in \(V_\omega\), not its arbitrary translation.\footnote{Translating the moving sofa \(S\) may invalidate the initial condition \(S \subseteq L_H\). To resolve this, we relax the \Cref{def:sofa} of a moving sofa \(S\) so that only some translation of \(S\) is required to be movable from \(L_H\) to \(L_V\) inside \(L\).} Then from (1), (2) and (3) above, we can always assume that \(S\) is contained in the intersection
\begin{equation}
\label{eqn:monotone}
\mathcal{M}(S) := H \cap V_\omega \cap \bigcap_{0 \leq t \leq \omega} L_t
\end{equation}
that we will define as the \emph{monotonization} of a moving sofa \(S\). The set \(\mathcal{M}(S)\) is also movable inside \(L\); observe that \(\mathcal{M}(S)\) is in each rotating hallway \(L_t\) of angle \(t \in [0, \omega]\), and see this in the perspective of the fixed hallway \(L\) instead of the moving hallway \(L_t\) and vary \(t\) from \(0\) to \(\omega\). So the monotonization \(\mathcal{M}(S)\) is a moving sofa containing \(S\) (\Cref{thm:monotonization-is-sofa})\footnote{This uses an implicit assumption that the intersection \(\mathcal{M}(S)\) should be connected. Indeed, \autocite{gerverMovingSofaCorner1992} assumes the connectedness of \(\mathcal{M}(S)\) in its proof of Theorem 1 of \autocite{gerverMovingSofaCorner1992} without further justification. We prove this assumption rigorously in \Cref{thm:monotonization-is-connected}.}, and we call such a sofa \(\mathcal{M}(S)\) from monotonization a \emph{monotone sofa} (\Cref{def:monotone-sofa}). Since any moving sofa \(S\) is contained in a larger monotone sofa \(\mathcal{M}(S)\), we only need to consider monotone sofas for the moving sofa problem.
